### 2023-03-28 omicron-generation.tex
homing (台大)

@@

>>>>

We assume that incubation periods and generation intervals follow a bivariate lognormal distribution---thus, we implicitly assume a power-law relationship between them. 
This was done because data were limited, and previous work \cite{sender2021unmitigated} has shown that this approach can also capture important aspects of the relationship.
In fact, however, previous studies have shown that mechanistic models capture this relationship better \citep{ferretti2020timing,hart2021}. 
When sufficient data are available, more mechanistic approaches may therefore be more suitable.

@@

\jd{Done quickly, needs cleaning (particularly cites).}
This study also has potential implications for studying generation times in population biology \citep{leslie1966intrinsic}.
Mean age of reproduction for a cohort of mothers corresponds to the forward generation distribution, while mean age of mothers for a cohort of offspring corresponds to the backward distribution.
Both could therefore be affected by dynamical considerations.
Similarly, the connection between generation times based at different recruitment stages is analogous to that between serial and generation intervals \citep{lebreton2005age,bienvenu2015new}.
Comparing definitions and methods across these fields could provide valuable future insights.
